%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape RAJESH KUMAR JENA} \\ \vspace{1pt}
    \small +91-7815010734 $|$ \href{mailto:x@x.com}{\underline{getrajeshkumarjena@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/rajesh-kumar-jena}} $|$
    \href{https://github.com/...}{\underline{github.com/Rajesh-1234567}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology}{Bhubanewar, Odisha}
      {Bachelor of technology in Computer Science, 2nd year}{Nov. 2022 -- April 2026}
      \resumeItem{Course Work : Design and analysis, Data Structure, Algorithms, OOPS, MicroProcessor, Digital Electronics, Machine Learning}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Summer Intern and Trainee}{June 2023 - Sept 2023 }
      {Evable India pvt. Ltd (Remote)}{Bhubaneswar, Odisha}
      \resumeItemListStart
        \resumeItem{Spearheaded the design and implementation of Project , a groundbreaking initiative aimed at seamlessly connecting users and optimizing payment workflows.}
        \resumeItem{Worked collaboratively within a dynamic team, fostering effective communication and contributing to a positive work environment.Acquired a profound understanding of software development methodologies, enhancing my proficiency.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Technical Head}{Sep. 2023 -- Present}
      {Coding Ninjas Student Chapter IIIT BBSR, GeeksForGeeks StudentChapter IIIT BBSR}{Bhubaneswar, Odisha}
      \resumeItemListStart
        \resumeItem{As the Technical Head of various Student Chapter at IIIT Bhubaneswar, I have spearheaded numerous initiatives aimed at fostering a culture of coding excellence and technical innovation among students. Through my leadership, I have played a pivotal role in organizing coding events, conducting coding sessions, and overseeing the development and maintenance of the chapter's website}
    \resumeItemListEnd
    \resumeSubheading
      {Student Ambassador}{Jan. 2023 -- Present}
      {Microsoft, GeeksForGeeks, Unstop, InternShala ISP, Nss IIT delhi}{Remote}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{HarvestHarbor} $|$ \emph{Flask, Python, Streamlit, Tensorflow, HTML, CSS, JS, Etheriun, Sapolia}}{Mar 2024}
          \resumeItemListStart
            \resumeItem{Led the comprehensive development of Harvest Harbor, a pioneering agricultural platform intertwining machine learning models, blockchain technology, and user-friendly interfaces. Orchestrated the integration of four ML models to predict fertilizer usage, recommend crops, detect diseases, and forecast yields. Additionally, crafted a seamless user interface employing HTML, CSS, and JavaScript, facilitating direct connections to government schemes and enabling farmers to buy and sell products securely through blockchain integration.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{WhatsApp Chat Analyzer} $|$ \emph{Python, Streamlit, Matplotlib, Pandas,WordCloud, Seaborn}}{Feb 2024 }
          \resumeItemListStart
            \resumeItem{The WhatsApp Chat Analyzer is a funny project, built with Python and libraries like Plotly and Pandas, analyzes chat data for insights. It offers features like message frequency analysis, word trends, and emoji analysis, aiding in child safety, parental monitoring, and mental health assessment. Deployed on Render and GitHub, it ensures easy access and data privacy.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL , JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: Flask, Django, Streamlit, Plotly} \\
     \textbf{Developer Tools}{: Git/Github, Azure, VS Code, Visual Studio, PyCharm, Jupyter, Android Studio, canva, Codeblocks} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Seaborn, Scikit-learn, TensorFlow, Requests}\\
     \textbf{Others}{: DBMS, Proble Solving, Project Management, Leadership, Teamwork, Public Speaking, Analytical Thinking}
    }}
 \end{itemize}


%-----------Achievements-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{- 4 Star Coder at CodeChef, rating - 1887 (Solved more than 250+ questions and have some global rank of 13, 21, 28, 47)} \\
     \textbf{- Leetcode, rating - 1592 (500+ questions solved)} \\
     \textbf{- Grand Master at CodeStudio, rating- 3000+ (1600+ solved)}\\
     \textbf{- HACKATHONS : Geekathon (top 8), Hackfest (Top 4)  }\\
     \textbf{- Campus Ambassador of Microsoft, GeeksForGeeks, Unstop, Nss IIT Delhi }\\
     \textbf{- Top Programming voice award by Linkedin (having 15k+ network connections ) }\\
     \textbf{- Google KickStart global rank - 3063}\\
     
    }}
 \end{itemize}
%
\end{document}